Holographic duality beyond AdS/CFT

### 2021-11-23 alpha/BeyondAdSCFT/beyondAdS.tex
Restructure notes on holography beyond AdS

% !TeX spellcheck = en_US
% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex
\documentclass[11pt,a4paper]{article}
\pdfoutput=1

\input{preamble.tex}

\usepackage{comment}
%\newcommand{\lui}[2]{\textcolor{red}{#1}\todo[color=yellow]{\scriptsize{L: #2}}}
\newcommand{\wei}[2]{\textcolor{magenta}{#1}\todo[color=yellow]{\scriptsize{WS: #2}}}
\newcommand{\wx}[2]{\textcolor{purple}{#1}\todo[color=teal]{\scriptsize{XL: #2}}}

\usepackage{xspace}
\newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}
\newcommand{\arcsinh}{\ensuremath{\mop{arcsinh}}}
\renewcommand{\tilde}[1]{\ensuremath{\widetilde{#1}}}
\newcommand{\ads}[1]{AdS\ensuremath{_{#1}}}
\newcommand{\cft}[1]{CFT\ensuremath{_{#1}}}

\usepackage{enumitem}

@@

%\author[a]{Wen-Xin Lai,}
\author[a]{Wei Song}

@@

%  \emailAdd{apolo@mail.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
%\flushbottom
\setlength{\parskip}{.5\baselineskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	Since the discovery of AdS/CFT duality \cite{Maldacena:1997re}, we have greatly furthered our understanding of quantum gravity in asymptotically AdS backgrounds. However, there are plenty of non-AdS geometries in our real worlds, including:
	\begin{itemize}%[noitemsep]
	\item The Kerr metric of a rotation black hole, \sidenote{which ... };
	\item The asymptotically flat / Minkowski spacetime, which well approximates our current universe at a smaller length (and time) scale;
	\item The asymptotically de Sitter spacetime, which well approximates our current (and future) universe at a larger length scale, and also during the period of inflation;
	\item The FRW metric (or more precisely, the Friedmann-Lemaître-Robertson-Walker \cite{Friedmann:1924bb,Lemaitre:1933gd,Robertson:1935zz,Walker:1937} metric), which describes the evolution of our homogeneous and isotropic universe from the big bang to its ;
	\item and more ...
	\end{itemize}
	Much less is known about quantum gravity in these backgrounds.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\bibliographystyle{JHEP} 
\bibliography{beyondAdS.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% !TeX spellcheck = en_US
% !TeX TS-program = pdflatex
% !BIB TS-program = biblatex
\documentclass[11pt,a4paper]{article}
\usepackage{jheppub}

\pdfoutput=1
\input{preamble.tex}

\usepackage{xspace}
\newcommand{\TTbar}{\texorpdfstring{\ensuremath{T\bar{T}}}{TTbar}\xspace}
\newcommand{\ads}[1]{AdS\ensuremath{_{#1}}}
\newcommand{\cft}[1]{CFT\ensuremath{_{#1}}}

@@

%\author[a]{Wen-Xin Lai,}
\author[a]{Wei Song}
%\author[a]{and Fengjun Xu}

@@

%\emailAdd{laiwx19@mails.tsinghua.edu.cn, wsong2014@mail.tsinghua.edu.cn}

@@

\begin{document}
\maketitle
%\flushbottom
\setlength{\parskip}{.5\baselineskip}

@@

	Since the discovery of AdS/CFT duality \cite{Maldacena:1997re}, we have greatly furthered our understanding of quantum gravity in asymptotically AdS backgrounds. However, there are plenty of non-AdS geometries in our real worlds, including:
	\begin{itemize}%[noitemsep]
	\item The Kerr metric of a rotation black hole, \sidenote{which ... };
	\item The asymptotically flat / Minkowski spacetime, which well approximates our current universe at a smaller length (and time) scale;
	\item The asymptotically de Sitter spacetime, which well approximates our current (and future) universe at a larger length scale, and also during the period of inflation;
	\item The FRW metric (or more precisely, the Friedmann-Lemaître-Robertson-Walker \cite{Friedmann:1924bb,Lemaitre:1933gd,Robertson:1935zz,Walker:1937} metric), which describes the evolution of our homogeneous and isotropic universe from the big bang to \sidenote{its ...} ;
	\item and more ...
	\end{itemize}
	Much less is known about quantum gravity in these backgrounds.

@@

\pagebreak
\bibliographystyle{JHEP} 
\bibliography{beyondAdS.bib}
